Covariates analysis of MSBB RNASeq (with two-step SVA)

### 2016-07-20 code/Rmd/MSSM_RNASeq_SVA_cdr.Rmd
Minor modifications

# Filter data
ind <- intersect(rownames(METADATA), colnames(COUNT))
ind <- setdiff(ind, 'hB_RNA_10622')
METADATA <- METADATA[ind,]
COUNT <- COUNT[, ind]
```
### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering, cache=TRUE}
# Max out age at 90
METADATA$AOD = gsub('\\+','',as.character(METADATA$AOD))

>>>>

# Filter data
ind <- intersect(rownames(METADATA), colnames(COUNT))
# ind <- setdiff(ind, 'hB_RNA_10622')
METADATA <- METADATA[ind,]
COUNT <- COUNT[, ind]
```
### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering, cache=TRUE}
# Max out age at 90
METADATA$AOD = gsub('\\+','',as.character(METADATA$AOD))
